---
title: "Uniform land protection targets may be inefficient at preserving the extent of undeveloped land and could cause substantial regional shifts in land use"
Authors: Alan V. Di Vittorio, Kanishka Narayan, Pralit Patel, Kate Calvin, Chris Vernon
output:
   html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    #toc_depth: 3
    #number_sections: false
    theme: cosmo
    #inverse: true
---



```{r, libraries& initializations,echo=FALSE, warning=FALSE, message=FALSE}
library(rgcam)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggsci)
library(parallel)
library(doParallel)
library(sf)
library(rgdal)
library(viridis)



#Define directories- 
#1. Path to header files,scripts
hdr_path <-"scripts/"

#2. Path to databses
db_path<-"databases/"

#3.Project name and date 
project_name<-"Protected area paper"
date <- date()
```

```{r, load support functions, echo=FALSE, message=FALSE, warning=FALSE}
# Load all support functions into memory
source( paste0(hdr_path,"diag_header.R"))	# configuration and helper functions
source( paste0(hdr_path,"diag_grapher.R"))  # functions to generate figures
source( paste0(hdr_path,"color_schemes.R" )) # some predefined color schemes
source( paste0(hdr_path,"diag_util_functions.R")) # library of useful utility functions
```


```{r,fig.height=14,fig.width=10,echo=FALSE,message=FALSE, warning=FALSE}
detach("package:plyr")

# Batch query results already saved to CSV to read
BATCH_QUERY_RESULTS <- c( )


low_availability_scenario <- c("Reference")
high_availability_scenario <- c("Reference")

QUERY_BATCH_FILE <- paste0("Verification_queries/Model_verification_queries_food_demand.xml")


tables_reference <- loadProject("project_files/tables_reference.proj")
tables_reference_high <- loadProject("project_files/tables_reference_high.proj")
#These is the range 
prot_constraints <- seq(0,100,by =10)

#Load all projects 
for(i in prot_constraints){
  
  assign(paste0("tables_",i,"prot"),loadProject(paste0("project_files/tables_",i,"prot.proj")))
  
}

# If the project files have been created, set this to TRUE
tables_created <- TRUE
```


```{r, create tables here, echo=FALSE, message=FALSE, warning=FALSE}

if (!tables_created){

  branch_db_conn<-localDBConn(paste0(db_path),paste0("database_basexdb"))
tables_reference<-addScenario(branch_db_conn, tables_reference, low_availability_scenario, QUERY_BATCH_FILE)

branch_db_conn<-localDBConn(paste0(db_path),paste0("database_basexdbhighavailability"))
tables_reference_high<-addScenario(branch_db_conn, tables_reference_high, high_availability_scenario, QUERY_BATCH_FILE)

for ( i in prot_constraints){
  
  branch_db_conn<-localDBConn(paste0(db_path),paste0("database_basexdb",i,"percprot"))
  
  assign(paste0("tables_",i,"prot"),addScenario(branch_db_conn, paste0("tables_",i,"prot.proj"), low_availability_scenario, QUERY_BATCH_FILE))
  
  
}
  
  }
```

```{r, add schemes, output folders, echo=FALSE, message=FALSE, warning=FALSE}

#Add constants for scheme
scheme_basic <- theme_bw() +
  theme(legend.text = element_text(size = 15)) +
  theme(legend.title = element_text(size = 15)) +
  theme(axis.text = element_text(size = 18)) +
  theme(axis.title = element_text(size = 18, face = "bold")) +
  theme(plot.title = element_text(size = 15, face = "bold", vjust = 1)) +
  theme(plot.subtitle = element_text(size = 9, face = "bold", vjust = 1))+ 
  theme(strip.text = element_text(size = 7))+
  theme(strip.text.x = element_text(size = 12, face = "bold"))+
  theme(strip.text.y = element_text(size = 15, face = "bold"))+
  theme(legend.position = "right")+
  theme(legend.text = element_text(size = 12))+
  theme(legend.title = element_text(size = 12,color = "black",face="bold"))+
  theme(axis.text.x= element_text(angle = 90,hjust=1))+
  theme(legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"))

theme0 <- theme(
  panel.border = element_rect(colour = "black", size=1),
  axis.text.y = element_text(angle = 0, color = "black", size = 15, margin = margin(r = 10)),
  axis.text.x = element_text(angle = 90, color = "black", size = 15, margin = margin(t = 10), vjust= 0.5),
  axis.title.y = element_text(size = 15, margin = margin(t = 0, r = 10, b = 0, l = 0)),
  axis.title.x = element_text(size = 15, margin = margin(t = 10, r = 0, b = 0, l = 0)),
  strip.text = element_text(size = 16),
  plot.title = element_text(hjust = 0.5,margin=margin(0,0,15,0)),
  legend.position="right", legend.justification = "center",
  legend.title = element_blank(),
  legend.key.size = unit(1.5, "cm"),
  legend.key.height=unit(1.5,"line"),
  legend.spacing.x = unit(1, 'cm'), 
  legend.background = element_blank()
)    

dir.create("outputs")
dir.create("outputs/csv")
dir.create("outputs/images")

output_path_csv <- "outputs/csv/"
output_path_images <- "outputs/images/"

SSP_spatial <- "Global"
spatial <- "Global"
```
# Figures

## Figure 1: Land allocation

### Land allocation shown here globally. For country level results, check the `outputs/images/land_allocation_plots/` folder in the root directory.

#### `Global land allocation by land type under different availability constraints. Dots represent the LOW availability scenario and diamonds represent the HIGH availability scenario.`

```{r, Land allocation plot, fig.width=12, fig.height=8,echo=FALSE, message=FALSE, warning=FALSE}

dir.create("outputs/images/land_allocation_plots/")
getQuery(tables_reference, "Aggregated Land Allocation") %>% 
       mutate(Availability = paste0("Low Availability"), policy ="CORE")->new_table

getQuery(tables_reference_high, "Aggregated Land Allocation") %>% 
       mutate(Availability = paste0("High Availability"), policy ="CORE")->new_table_high

new_table <- bind_rows(new_table,new_table_high)

for (i in prot_constraints){
  
  new_table %>% bind_rows(getQuery(get(paste0("tables_",i,"prot")), "Aggregated Land Allocation") %>% 
       mutate(Availability = paste0(100-i," percent"), policy ="CORE"))->new_table
  
}


plot_type <-"barplot"
#Land allocation
landuse.d <- new_table  
landuse.d$agg.land <- landuse.d[["land-allocation"]]
landuse.d[landuse.d[,"land-allocation"] == "grass", "agg.land"] <- "Grassland"
landuse.d[landuse.d[,"land-allocation"] == "pasture (other)", "agg.land"] <- "Grassland"
landuse.d[landuse.d[,"land-allocation"] == "otherarable", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "RootTuber", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "crops", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "biomassGrass", "agg.land"] <- "Biomass"
landuse.d[landuse.d[,"land-allocation"] == "biomassTree", "agg.land"] <- "Biomass"
landuse.d[landuse.d[,"land-allocation"] == "tundra", "agg.land"] <- "desert"
landuse.d[landuse.d[,"land-allocation"] == "rock and desert", "agg.land"] <- "desert"
landuse.d[landuse.d[,"land-allocation"] == "forest (managed)", "agg.land"] <- "Forests (Harvested)"
landuse.d[landuse.d[,"land-allocation"] == "forest (unmanaged)", "agg.land"] <- "Forests (Unmanaged)"
landuse.d[landuse.d[,"land-allocation"] == "pasture (grazed)", "agg.land"] <- "Grazed Pasture"
landuse.d[landuse.d[,"land-allocation"] == "shrubs", "agg.land"] <- "Shrubland"
stopifnot(sum(is.na(landuse.d$agg.land)) == 0)
#landuse.d$agg.land <- factor(landuse.d$agg.land, levels=names(PAL_landuse))
landuse.d %>%
    group_by(Availability,region,year,policy,agg.land) %>%
    mutate(value=sum(value)) %>%
     ungroup() %>%
     dplyr::select(Availability,region,year,policy,agg.land,value) %>%
     distinct()->landuse.d



landuse.d <- add_global_sum(landuse.d)
landplot<-landuse.d %>% filter(!agg.land %in% c("desert","urban"))
landplot[TITLE_FIELD_NAME] <- "Land Use by Type"

landplot <- landuse.d %>% filter(!agg.land %in% c("desert","urban"))


landplot$Availability <- factor(landplot$Availability, levels = c("0 percent", "10 percent", "20 percent","30 percent","40 percent","50 percent","60 percent","70 percent","80 percent", "90 percent", "100 percent", "High Availability", "Low Availability"))


p <- ggplot(landplot %>% filter(region=="Global",
                                !Availability %in% c("Low Availability", "High Availability"))) + geom_line(data=landplot%>% filter(region=="Global",
                                          !Availability %in% c("Low Availability", "High Availability")                                                                                                     ),aes(x=year, y=value, color=Availability), size=1.2) +
  geom_line(data=landplot %>% filter(Availability == "Low Availability",region=="Global"),aes(x=year, y=value), color="grey",size=1.3,alpha=0.6, show.legend = FALSE)+
  geom_point(data=landplot %>% filter(Availability == "Low Availability",region=="Global"),aes(x=year, y=value), color="black",size=1.3,alpha=0.6, show.legend = FALSE)+
geom_line(data=landplot %>% filter(Availability == "High Availability",region=="Global"),aes(x=year, y=value), color="grey", show.legend = FALSE,size=1.3,alpha=0.6)+
  geom_point(data=landplot %>% filter(Availability == "High Availability",region=="Global"),aes(x=year, y=value), color="black",shape=18, show.legend = FALSE,size=1.3,alpha=0.6)+
facet_wrap(~agg.land,scales = "free")+ylab("thousand km2")+ggtitle("Land allocation by type under different availability constraints ")+labs(subtitle=paste0("Regions-",toString("Global"),". Points are the Low Availability scenario, diamonds are the High Availability scenario."))+
scale_color_viridis(discrete = TRUE, option = "D")  

p+scheme_basic


ggsave( paste0("outputs/images/land_allocation_plots/",'1. Land allocation by type ',project_name,toString("Global"),'.png'),width = 10, height = 10)


write.csv(landplot,paste0(output_path_csv ,'1. Land allocation by type',project_name,"all regions",'.csv'))
```


## Figure 2: Crop production by type


### Crop production shown here globally. For country level results, check the `outputs/images/crop_production_plots/` folder in the root directory.

#### `Global crop and commodity production under different land availability constraints. Dots represent the LOW availability scenario and diamonds represent the HIGH availability scenario.`

```{r, crop production, fig.width=12, fig.height=8,echo=FALSE,message=FALSE, warning=FALSE}
dir.create("outputs/images/crop_production_plots/")

getQuery(tables_reference, "Ag Production by Crop Type") %>% 
       mutate(Availability = paste0("Low Availability"), policy ="CORE")->new_table


getQuery(tables_reference_high, "Ag Production by Crop Type") %>% 
       mutate(Availability = paste0("High Availability"), policy ="CORE")->new_table_high


new_table <- bind_rows(new_table, new_table_high)

for (i in prot_constraints){
  
  new_table %>% bind_rows(getQuery(get(paste0("tables_",i,"prot")), "Ag Production by Crop Type") %>% 
       mutate(Availability = paste0(100 - i," percent"), policy ="CORE"))->new_table
  
}

crop <- bind_rows(new_table) %>% 
        group_by(region,Availability,policy,output,year) %>% 
        mutate(value=sum(value)) %>% 
        ungroup() %>% 
        select(region,Availability,policy,output,year,value) %>% 
        distinct() %>% 
        add_global_sum() %>% 
        #filter(region %in% spatial) %>% 
        filter(!output %in% c("UnmanagedLand","NonFoodDemand_Forest"))

crop$Availability <- factor(crop$Availability, levels = c("0 percent", "10 percent", "20 percent","30 percent","40 percent","50 percent","60 percent","70 percent","80 percent", "90 percent", "100 percent", "High Availability", "Low Availability"))
for (i in unique(c("Global"))){
p <- ggplot(crop %>% filter(region==i)) + geom_line(data=crop %>% filter(!Availability %in% c("Low Availability", "High Availability"),region ==i),aes(x=year, y=value, color=Availability), size=1.2)   +facet_wrap(~output,scales = "free_y")+
geom_point(data=crop %>% filter(Availability == "Low Availability",
                                region==i),aes(x=year, y=value), color="black", show.legend = FALSE,alpha=0.5)+
geom_line(data=crop %>% filter(Availability == "Low Availability",
                               region==i),aes(x=year, y=value), color="grey", show.legend = FALSE)+  
geom_point(data=crop %>% filter(Availability == "High Availability",
                                region==i),aes(x=year, y=value), color="black", show.legend = FALSE, shape=18,alpha=0.5)+
geom_line(data=crop %>% filter(Availability == "High Availability",
                               region==i),aes(x=year, y=value), color="black", show.legend = FALSE, color="grey")+  
ylab("Mt (EJ for biomass)")+ggtitle("Crop production")+labs(subtitle=paste0("Regions-",toString(i),". Points represent the low availability scenario, diamonds represent the high availability scenario"))+
scale_color_viridis(discrete = TRUE, option="D")  

p+scheme_basic


ggsave( paste0("outputs/images/crop_production_plots/",'2. Crop production by type',project_name,toString(i),'.png'),width = 14, height = 10)}


write.csv(crop ,paste0(output_path_csv ,'2. Crop production scenarios all regions',toString(i),'.csv'))

p+scheme_basic

```


## Figure 3: Primary energy

#### `Primary energy consumption under different land availability constraints.`

```{r, Primary Energy, fig.width=12, fig.height=8,echo=FALSE,message=FALSE, warning=FALSE}


getQuery(tables_reference, "primary energy consumption by region (direct equivalent)") %>% 
       mutate(Availability = paste0("Low Availability"), policy ="CORE")->new_table

getQuery(tables_reference_high, "primary energy consumption by region (direct equivalent)") %>% 
       mutate(Availability = paste0("High Availability"), policy ="CORE")->new_table_high

new_table <- bind_rows(new_table,new_table_high)

for (i in prot_constraints){
  
  new_table %>% bind_rows(getQuery(get(paste0("tables_",i,"prot")), "primary energy consumption by region (direct equivalent)") %>% 
       mutate(Availability = paste0(100-i," percent"), policy ="CORE"))->new_table
  
}

energy_master<-new_table%>% 
                     add_global_sum() %>% 
                     filter(region %in% SSP_spatial) %>% 
                     group_by(region,Availability,year,fuel) %>% 
                     mutate(value=sum(value)) %>% 
                     ungroup() %>% 
                     dplyr::select(region, Availability,year,value,fuel) %>% 
                     distinct() %>% 
                     filter(year>2010)    
energy_master_total <- energy_master %>% 
                       group_by(region,Availability,year) %>% 
                       mutate(value=sum(value),
                              fuel= "n total energy") %>% 
                       ungroup() %>% 
                      distinct()
energy_master <- bind_rows(energy_master, energy_master_total) %>% 
                 mutate(fuel = if_else(fuel=="traded coal","k traded coal",fuel),
                        fuel = if_else(fuel=="traded natural gas","l traded natural gas",fuel),
                        fuel = if_else(fuel=="traded oil","m traded oil",fuel))

`%notin%` <- Negate(`%in%`)

energy_master$Availability <- factor(energy_master$Availability, levels = c("0 percent", "10 percent", "20 percent","30 percent","40 percent","50 percent","60 percent","70 percent","80 percent", "90 percent", "100 percent", "High Availability", "Low Availability"))
p <- ggplot() + geom_line(data=energy_master %>% filter(!Availability %in% c("Low Availability",
                                                                             "High Availability")),aes(x=year, y=value, color=Availability), size=1.2)+ 
    geom_point(data=energy_master %>% filter(Availability == "Low Availability"),aes(x=year, y=value), color="black", show.legend = FALSE)+
  geom_line(data=energy_master %>% filter(Availability == "Low Availability"),aes(x=year, y=value), color="grey", show.legend = FALSE)+
    geom_point(data=energy_master %>% filter(Availability == "High Availability"),aes(x=year, y=value), color="black", show.legend = FALSE, shape=18)+
  geom_line(data=energy_master %>% filter(Availability == "High Availability"),aes(x=year, y=value), color="black", show.legend = FALSE)+
    facet_wrap(~fuel,scales = "free_y")+ylab("EJ")+ggtitle("Primary energy consumption ")+labs(subtitle=paste0("Regions-",toString(SSP_spatial),". Dots are the Low Avail. scenario, Diamonds are the High Avail. scenario"))+
  scale_color_viridis(discrete = TRUE, option="D")



ggsave( paste0(output_path_images,"3.primary energy consumption in EJ SSP",project_name,'.png'),width = 14, height = 12)

write.csv(energy_master, paste0(output_path_csv,"3. Primary_energy_table.csv"))

p+scheme_basic
```

## Figure 4: Prices

### Only Wheat regional prices shown here. For other commodity prices check `outputs/images/price_plots/` folder in root directory.
```{r,fig.width=12, fig.height=8,echo=FALSE,message=FALSE, warning=FALSE}

dir.create("outputs/images/price_plots/")
dir.create("outputs/csv/price_data/")
getQuery(tables_reference, "ag commodity prices") %>% 
       mutate(Availability = paste0("Low Availability"), policy ="CORE")->new_table


getQuery(tables_reference_high, "ag commodity prices") %>% 
       mutate(Availability = paste0("High Availability"), policy ="CORE")->new_table_high

new_table <- bind_rows(new_table,new_table_high)


new_table$Availability <- factor(new_table$Availability, levels = c("0 percent", "10 percent", "20 percent","30 percent","40 percent","50 percent","60 percent","70 percent","80 percent", "90 percent", "100 percent", "High Availability", "Low Availability"))


for (i in prot_constraints){
  
  new_table %>% bind_rows(getQuery(get(paste0("tables_",i,"prot")), "ag commodity prices") %>% 
       mutate(Availability = paste0(100-i," percent"), policy ="CORE"))->new_table
  
}

new_table ->ag_price_table


ag_price_table$Availability <- factor(ag_price_table$Availability, levels = c("0 percent", "10 percent", "20 percent","30 percent","40 percent","50 percent","60 percent","70 percent","80 percent", "90 percent", "100 percent", "High Availability", "Low Availability"))
for(i in unique(c("Wheat"))){

g <- ggplot(data= ag_price_table %>% filter(year>=2015, sector == i)%>% filter(!Availability %in% c("Low Availability",
                                                                             "High Availability")), aes(x=year,y=value,color=Availability))+
     geom_line( size=1.2, alpha=0.6)+
     geom_line(data=ag_price_table %>% filter(Availability == "Low Availability", sector==i),aes(x=year, y=value), color="grey", show.legend = FALSE)+
     geom_point(data=ag_price_table %>% filter(Availability == "Low Availability",sector==i),aes(x=year, y=value), color="black", show.legend = FALSE)+
     geom_point(data=ag_price_table %>% filter(Availability == "High Availability",sector==i),aes(x=year, y=value), color="black", show.legend = FALSE, shape=18)+
     ylab("$/kg for crops, $/GJ for biomass")+
     ggtitle(paste0("Domestic producer ", toString(i), " prices under the CORE scenarios"))+
     facet_wrap(~region,scales= "free_y")+
     scale_color_viridis(discrete = TRUE, option="D")+
     geom_line(data=ag_price_table %>% filter(Availability == "High Availability",sector==i),aes(x=year, y=value), color="grey", show.legend = FALSE)+
    labs(subtitle = "Dots are the Low Avail. scenario, Diamonds are the High Avail. scenario")

g+ scheme_basic +                                                                
  theme(strip.text.x = element_text(size = 12))

write.csv(ag_price_table,paste0("outputs/csv/price_data/","4. Prices for",toString(i),".csv"))
ggsave( paste0("outputs/images/price_plots/",'4. Prices for',project_name,toString(i),'.png'),width = 24, height = 20)


}
g+ scheme_basic +                                                                
  theme(strip.text.x = element_text(size = 9))
```

## Figure 5: Change in land allocation by types in 2050 (scatterplot)

### Scatterplot shown here for Crops. For other land types check the `outputs/images/marginal_scatterplots/` folder in the root directory.

#### `Change in land allocation by 2050. are percent change relative to 2015.The blue dots represent each GCAM region, and the black dots represent the global values.`

```{r,fig.width=12, fig.height=8,echo=FALSE,message=FALSE, warning=FALSE}
dir.create("outputs/images/marginal_scatterplots/")
getQuery(tables_reference, "Aggregated Land Allocation") %>% 
       mutate(Availability = paste0("Low"), policy ="CORE")->new_table

getQuery(tables_reference_high, "Aggregated Land Allocation") %>% 
       mutate(Availability = paste0("High"), policy ="CORE")->new_table_high

new_table <- bind_rows(new_table,new_table_high)
for (i in prot_constraints){
  
  new_table %>% bind_rows(getQuery(get(paste0("tables_",i,"prot")), "Aggregated Land Allocation") %>% 
       mutate(Availability = paste0(100-i," percent"), policy ="CORE"))->new_table
  
}

new_table %>% 
  group_by(scenario,year,Availability,`land-allocation`) %>% 
  mutate(value=sum(value),
         region="autGlobal") %>%
  ungroup() %>% 
  distinct()->new_table_global
  

new_table %>% 
  left_join(new_table_global %>% select(-region)%>%  rename(global_value=value)) %>% 
  filter(year ==2050, !`land-allocation`%in%c("tundra","urban","rock and desert"))->new_table_2050


new_table %>% 
  left_join(new_table_global %>% select(-region) %>%  rename(global_value=value)) %>%
  filter(year ==2025) %>% 
  select(region,`land-allocation`,hist_value =value,hist_global_value=global_value) %>% 
  distinct()->new_table_2015

new_table_2050 %>% 
  left_join(new_table_2015) %>% 
  mutate(hist_value = if_else(is.na(hist_value),0,hist_value),
         hist_global_value = if_else(is.na(hist_global_value),0,hist_global_value))->new_table_consolidated


landuse.d <- new_table_consolidated  
  
landuse.d[landuse.d[,"land-allocation"] == "grass", "agg.land"] <- "Grassland"
landuse.d[landuse.d[,"land-allocation"] == "pasture (other)", "agg.land"] <- "Grassland"
landuse.d[landuse.d[,"land-allocation"] == "otherarable", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "RootTuber", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "crops", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "biomassGrass", "agg.land"] <- "Biomass"
landuse.d[landuse.d[,"land-allocation"] == "biomassTree", "agg.land"] <- "Biomass"
landuse.d[landuse.d[,"land-allocation"] == "tundra", "agg.land"] <- "desert"
landuse.d[landuse.d[,"land-allocation"] == "rock and desert", "agg.land"] <- "desert"
landuse.d[landuse.d[,"land-allocation"] == "forest (managed)", "agg.land"] <- "Forests (Harvested)"
landuse.d[landuse.d[,"land-allocation"] == "forest (unmanaged)", "agg.land"] <- "Forests (Unmanaged)"
landuse.d[landuse.d[,"land-allocation"] == "pasture (grazed)", "agg.land"] <- "Grazed Pasture"
landuse.d[landuse.d[,"land-allocation"] == "shrubs", "agg.land"] <- "Shrubland"
stopifnot(sum(is.na(landuse.d$agg.land)) == 0)

landuse.d[landuse.d == Inf] <- 100


landuse.d %>% 
    group_by(Availability,region,year,policy,agg.land) %>% 
    mutate(value=(((sum(value)-sum(hist_value)))/sum(hist_value))*100,
           global_value=(((sum(global_value)-sum(hist_global_value)))/sum(hist_global_value))*100) %>%
     ungroup() %>% 
  mutate(value = if_else(is.na(value),0,value)) %>% 
   group_by(Availability,year,policy,agg.land) %>% 
    mutate(mean_value = mean(global_value)) %>% 
   ungroup() %>% 
     dplyr::select(Availability,region,year,policy,agg.land,value,mean_value) %>% 
    distinct() %>% 
  arrange(agg.land, mean_value)->landuse.d




for(i in c("Crops")){

    
  
g <- ggplot()+
     geom_jitter(data= landuse.d %>% filter(region!="autGlobal", agg.land ==i), aes(x=reorder(Availability,mean_value) , y=value), color="blue",width=0.1,size=0.8,alpha=0.5)+
     geom_point(data= landuse.d %>% filter(region=="USA", agg.land ==i), aes(x= reorder(Availability,mean_value), y=mean_value),color="black",show.legend = FALSE,size=2)+
     xlab("Availability")+
     ylab("Percent change in land allocated by 2050")+
     labs(subtitle= "Blue dots represent each region in GCAM, black dots represent mean across regions")+
     ggtitle(paste0("LT-",i))+
    facet_wrap(~agg.land,scales="free")+
   geom_col()
    

g+ scheme_basic


name <- gsub("/","_",i)
ggsave( paste0("outputs/images/marginal_scatterplots/","5.Change in land allocation in 2050 across constraints",toString(name),project_name,'.png'),width = 10, height = 6)

}


write.csv(landuse.d %>% rename(global_value=mean_value), paste0(output_path_csv,"5. Change in land allocation in 2050 across constraints ","all_LT",".csv"))
g+ scheme_basic
```


## Figure 6a: Marginal change in land allocation vs Marginal change in availability (thous km2)

#### `Marginal absolute changes in land allocation in 2050 due to incremental decreases in land availability, globally. The x-axis denotes a 10% decrease in land availability from the previous tic, starting at 100% availability. The y-axis values are absolute change in area relative to that at the previous availability level. Circles indicate the current availability and extent of unmanaged forest, grassland, shrubland, respectively, and of these three types combined (on the managed land type lines), based on the 2015 GCAM initial state. The triangles indicate land type availability and extent when protected area is approximately doubled. The absolute change in land allocation of a particular type due to meeting the new protection target is estimated by moving from the circle to the triangle along a given line.`

```{r,fig.width=12, fig.height=8,echo=FALSE,message=FALSE, warning=FALSE}

region_select <- "Global"

getQuery(tables_reference, "Aggregated Land Allocation") %>% 
       mutate(Protection = paste0("High"), policy ="CORE")->new_table

getQuery(tables_reference_high, "Aggregated Land Allocation") %>% 
       mutate(Protection = paste0("Low"), policy ="CORE")->new_table_high


new_table <- bind_rows(new_table)
for (i in prot_constraints){
  
  new_table %>% bind_rows(getQuery(get(paste0("tables_",i,"prot")), "Aggregated Land Allocation") %>% 
       mutate(Protection = paste0(i," percent"), policy ="CORE"))->new_table
  
}

new_table %>% 
  group_by(`land-allocation`, year,Protection) %>% 
  mutate(value = sum(value),
         region = "Global") %>% 
  ungroup() %>% 
  distinct()->new_table_global
  

new_table %>% 
  bind_rows(new_table_global) %>% 
  filter(year %in% c(2050)) ->new_table_2050


new_table %>%
  bind_rows(new_table_global) %>% 
  filter(year ==2025) %>% 
  select(region,`land-allocation`,hist_value =value) %>% 
  distinct()->new_table_2015

new_table_2050 %>% 
  left_join(new_table_2015) %>% 
  mutate(value= ((value)))->new_table_2

landuse.d <- new_table_2  
  

landuse.d$agg.land <- landuse.d[["land-allocation"]]
landuse.d[landuse.d[,"land-allocation"] == "grass", "agg.land"] <- "Grassland"
landuse.d[landuse.d[,"land-allocation"] == "pasture (other)", "agg.land"] <- "Grassland"
landuse.d[landuse.d[,"land-allocation"] == "otherarable", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "RootTuber", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "crops", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "biomassGrass", "agg.land"] <- "Biomass"
landuse.d[landuse.d[,"land-allocation"] == "biomassTree", "agg.land"] <- "Biomass"
landuse.d[landuse.d[,"land-allocation"] == "tundra", "agg.land"] <- "desert"
landuse.d[landuse.d[,"land-allocation"] == "rock and desert", "agg.land"] <- "desert"
landuse.d[landuse.d[,"land-allocation"] == "forest (managed)", "agg.land"] <- "Forests (Harvested)"
landuse.d[landuse.d[,"land-allocation"] == "forest (unmanaged)", "agg.land"] <- "Forests (Unmanaged)"
landuse.d[landuse.d[,"land-allocation"] == "pasture (grazed)", "agg.land"] <- "Grazed Pasture"
landuse.d[landuse.d[,"land-allocation"] == "shrubs", "agg.land"] <- "Shrubland"
stopifnot(sum(is.na(landuse.d$agg.land)) == 0)


landuse.d %>% 
    group_by(Protection,region,year,policy,agg.land) %>% 
    mutate(value=((sum(value))),
           hist_value = sum(hist_value)) %>%
     ungroup() %>% 
     dplyr::select(Protection,region,year,policy,agg.land,value,hist_value) %>% 
    distinct()->landuse.d

landuse.d %>% 
  distinct() %>%
  select(-hist_value) %>% 
  spread(Protection,value) %>%
  left_join(landuse.d %>% filter(Protection %in% c("High")) %>% select(region, agg.land, hist_value) %>% distinct()) %>% 
  mutate(`100 percent`=  (`100 percent`- `90 percent`),
         `90 percent`=  (`90 percent`- `80 percent`),
         `80 percent`=  (`80 percent`- `70 percent`),
         `70 percent`=  (`70 percent`- `60 percent`),
         `60 percent`=  (`60 percent`- `50 percent`),
         `50 percent`=  (`50 percent`- `40 percent`),
         `40 percent`=  (`40 percent`- `30 percent`),
         `30 percent`=  (`30 percent`- `20 percent`),
         `20 percent`=  (`20 percent`- `10 percent`),
         `10 percent`=  (`10 percent`- `0 percent`)
         ) %>% 
    select(-`0 percent`, -High) %>% 
  gather("Protection","value","10 percent":"90 percent") %>% 
  filter(year%in% c(2050)) %>% 
  mutate(value = value) %>% 
  mutate(Protection= as.integer(gsub(" percent","",Protection)))->data_for_plot

low_avail_details <- read.csv("other_data/land_convertible.csv",stringsAsFactors = FALSE) %>% select(-Needed_unprotected_percent_convertible,-new_unmanaged) %>% 
          mutate(available=100-available)


needed <- read.csv("other_data/land_convertible.csv",stringsAsFactors = FALSE) %>% 
          select(-available,-Needed_unprotected_percent_convertible) %>% 
          distinct() %>% 
          mutate(new_unmanaged=100-new_unmanaged)

avail_managed <-  read.csv("other_data/available_managed.csv",stringsAsFactors = FALSE) %>% dplyr::select(-Needed_unprotected_percent_convertible,-needed_managed) %>% 
                  distinct() %>% 
                  mutate(new_managed= 100-new_managed) 


needed_managed <- read.csv("other_data/available_managed.csv",stringsAsFactors = FALSE) %>% 
                  dplyr::select(-Needed_unprotected_percent_convertible,-new_managed) %>% 
                  distinct() %>% 
                  mutate(needed_managed= 100-needed_managed)

data_for_plot %>% left_join(low_avail_details) %>% mutate(available= available) %>% 
  left_join(avail_managed, by = c("region")) %>% 
  left_join(needed, by = c("region","agg.land")) %>% 
  left_join(needed_managed, by =c("region")) %>% 
  mutate(new_unmanaged=if_else(is.na(new_unmanaged),needed_managed,new_unmanaged),
         available= if_else(is.na(available),new_managed,available))->data_for_plot


formatter1000 <- function(x){ 
    100-x 
}



intersection_points <- data_for_plot %>% 
                       group_by(region,agg.land) %>% 
                       mutate(diff = abs(available- Protection)) %>% 
                       filter(diff < 10) %>% 
                       mutate(value = mean(value),
                              Protection=available) %>% 
                       ungroup() %>% 
                       distinct()

intersection_points_needed <- data_for_plot %>% 
                       group_by(region,agg.land) %>% 
                       mutate(diff = abs(new_unmanaged- Protection)) %>% 
                       filter(diff < 12) %>% 
                       mutate(value = mean(value),
                              Protection=new_unmanaged) %>% 
                       ungroup() %>% 
                       distinct()

data_for_plot %>% filter(agg.land=="biomass")->biomass_data

g <- ggplot()+
   geom_point(data=intersection_points %>% na.omit() %>%  
                filter(region==region_select,!agg.land %in% c("rock and desert", "urban","desert")),
             aes(x=available,y=value,color=agg.land),size=4)+
  geom_point(data=intersection_points_needed %>% filter(region==region_select,!agg.land %in% c("rock and desert", "urban","desert")),aes(x=new_unmanaged,y=value,color=agg.land),show.legend = FALSE,shape=17,size=4) +
  geom_line(data=data_for_plot%>% 
               filter(region==region_select,
                      !agg.land %in% c("rock and desert", "urban","desert")),
            aes(x=Protection,y=value,color=agg.land,group=agg.land))+
  # geom_vline(data=data_for_plot %>% na.omit() %>% filter(region==region_select),aes(xintercept=available,color=agg.land), linetype = 3,size=2,show.legend = FALSE) +
  facet_wrap(~region,scales="free_y")+
  ylab("Marginal increase/decrease in thous km2")+
  xlab("Availability")+
  ggtitle("Marginal increase/decrease in land allocation by land type in 2050 with increase in protection")+
  scale_color_lancet()+
  guides(color=guide_legend(title="Land type"))+
  scale_shape_manual(values=c(0,1,2))+scale_x_continuous(labels=formatter1000,breaks = seq(0,100,10),minor_breaks = seq(0, 100, 10))+
  labs(subtitle = "Dots are the starting percent of available land in 2015.Triangles are new percentage of available land after implementing 30 by 30 targets.")

g + scheme_basic+
  theme(axis.line = element_line(color='black'),
    plot.background = element_blank())

ggsave( paste0(output_path_images,"6.Change in land allocation in 2050",project_name,toString(region_select),'.png'),width = 16, height = 14)

write.csv(data_for_plot, paste0(output_path_csv,"6. Marginal_plot_thouskm2.csv"))


```

## Figure 6b: Marginal change in land allocation vs Marginal change in availability (thous km2) all regions


```{r,fig.width=12, fig.height=8,echo=FALSE,message=FALSE, warning=FALSE}

g <- ggplot()+
   geom_point(data=intersection_points %>% na.omit() %>%  
                filter(!agg.land %in% c("rock and desert", "urban","desert")),
             aes(x=available,y=value,color=agg.land),size=2)+
  geom_point(data=intersection_points_needed %>% filter(!agg.land %in% c("rock and desert", "urban","desert")),aes(x=new_unmanaged,y=value,color=agg.land),show.legend = FALSE,shape=17,size=2) +
  geom_line(data=data_for_plot%>% 
               filter(
                      !agg.land %in% c("rock and desert", "urban","desert")),
            aes(x=Protection,y=value,color=agg.land,group=agg.land))+
  # geom_vline(data=data_for_plot %>% na.omit() %>% filter(region==region_select),aes(xintercept=available,color=agg.land), linetype = 3,size=2,show.legend = FALSE) +
  facet_wrap(~region,scales="free_y")+
  ylab("Marginal increase/decrease in thous km2")+
  xlab("Availability")+
  ggtitle("Marginal increase/decrease in land allocation by land type in 2050 with increase in protection")+
  scale_color_lancet()+
  guides(color=guide_legend(title="Land type"))+
  scale_shape_manual(values=c(0,1,2))+scale_x_continuous(labels=formatter1000,breaks = seq(0,100,10),minor_breaks = seq(0, 100, 10))+
  labs(subtitle = "Dots are the starting percent of available land in 2015.Triangles are new percentage of available land after implementing 30 by 30 targets.")

g + scheme_basic+
  theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    axis.text=element_text(size=10),
    strip.text.x = element_text(size = 8))

ggsave( paste0(output_path_images,"6.Change in land allocation in 2050 all regions thous km2",project_name,'.png'),width = 16, height = 14)

#write.csv(data_for_plot, paste0(output_path_csv,"6. Marginal_plot_thouskm2.csv"))
```



## Figure 6c: Marginal change in land allocation vs Marginal change in availability (Percent)

#### `Marginal relative changes in land allocation in 2050 due to incremental decreases in land availability, globally. The x-axis denotes a 10% decrease in land availability from the previous tic, starting at 100% availability. The y-axis values are percent change in land type area relative to that at the previous availability level. Circles indicate the current availability and extent of unmanaged forest, grassland, shrubland, respectively, and of these three types combined (on the managed land type lines), based on the 2015 GCAM initial state. The triangles indicate land type availability and extent when protected area is approximately doubled. The relative change in land allocation of a particular type due to meeting the new protection target is estimated by moving from the circle to the triangle along a given line.`


```{r,fig.width=12, fig.height=8,echo=FALSE,message=FALSE, warning=FALSE}

region_select <- "Global"

getQuery(tables_reference, "Aggregated Land Allocation") %>% 
       mutate(Protection = paste0("High"), policy ="CORE")->new_table

getQuery(tables_reference_high, "Aggregated Land Allocation") %>% 
       mutate(Protection = paste0("Low"), policy ="CORE")->new_table_high


new_table <- bind_rows(new_table)
for (i in prot_constraints){
  
  new_table %>% bind_rows(getQuery(get(paste0("tables_",i,"prot")), "Aggregated Land Allocation") %>% 
       mutate(Protection = paste0(i," percent"), policy ="CORE"))->new_table
  
}

new_table %>% 
  group_by(`land-allocation`, year,Protection) %>% 
  mutate(value = sum(value),
         region = "Global") %>% 
  ungroup() %>% 
  distinct()->new_table_global
  

new_table %>% 
  bind_rows(new_table_global) %>% 
  filter(year %in% c(2050)) ->new_table_2050


new_table %>%
  bind_rows(new_table_global) %>% 
  filter(year ==2025) %>% 
  select(region,`land-allocation`,hist_value =value) %>% 
  distinct()->new_table_2015

new_table_2050 %>% 
  left_join(new_table_2015) %>% 
  mutate(value= ((value)))->new_table_2

landuse.d <- new_table_2  
  
landuse.d$agg.land <- landuse.d[["land-allocation"]]
landuse.d[landuse.d[,"land-allocation"] == "grass", "agg.land"] <- "Grassland"
landuse.d[landuse.d[,"land-allocation"] == "pasture (other)", "agg.land"] <- "Grassland"
landuse.d[landuse.d[,"land-allocation"] == "otherarable", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "RootTuber", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "crops", "agg.land"] <- "Crops"
landuse.d[landuse.d[,"land-allocation"] == "biomassGrass", "agg.land"] <- "Biomass"
landuse.d[landuse.d[,"land-allocation"] == "biomassTree", "agg.land"] <- "Biomass"
landuse.d[landuse.d[,"land-allocation"] == "tundra", "agg.land"] <- "desert"
landuse.d[landuse.d[,"land-allocation"] == "rock and desert", "agg.land"] <- "desert"
landuse.d[landuse.d[,"land-allocation"] == "forest (managed)", "agg.land"] <- "Forests (Harvested)"
landuse.d[landuse.d[,"land-allocation"] == "forest (unmanaged)", "agg.land"] <- "Forests (Unmanaged)"
landuse.d[landuse.d[,"land-allocation"] == "pasture (grazed)", "agg.land"] <- "Grazed Pasture"
landuse.d[landuse.d[,"land-allocation"] == "shrubs", "agg.land"] <- "Shrubland"
stopifnot(sum(is.na(landuse.d$agg.land)) == 0)


landuse.d %>% 
    group_by(Protection,region,year,policy,agg.land) %>% 
    mutate(value=((sum(value))),
           hist_value = sum(hist_value)) %>%
     ungroup() %>% 
     dplyr::select(Protection,region,year,policy,agg.land,value,hist_value) %>% 
    distinct()->landuse.d

landuse.d %>% 
  distinct() %>%
  select(-hist_value) %>% 
  spread(Protection,value) %>%
  left_join(landuse.d %>% filter(Protection %in% c("High")) %>% select(region, agg.land, hist_value) %>% distinct()) %>% 
  mutate(`100 percent`=  ((`100 percent`- `90 percent`)/`90 percent`)*100,
         `90 percent`=  ((`90 percent`- `80 percent`)/`80 percent`)*100,
         `80 percent`=  ((`80 percent`- `70 percent`)/`70 percent`)*100,
         `70 percent`=  ((`70 percent`- `60 percent`)/`60 percent`)*100,
         `60 percent`=  ((`60 percent`- `50 percent`)/`50 percent`)*100,
         `50 percent`=  ((`50 percent`- `40 percent`)/`40 percent`)*100,
         `40 percent`=  ((`40 percent`- `30 percent`)/`30 percent`)*100,
         `30 percent`=  ((`30 percent`- `20 percent`)/`20 percent`)*100,
         `20 percent`=  ((`20 percent`- `10 percent`)/`10 percent`)*100,
         `10 percent`=  ((`10 percent`- `0 percent`)/`0 percent`)*100
         ) %>% 
    select(-`0 percent`, -High) %>% 
  gather("Protection","value","10 percent":"90 percent") %>% 
  filter(year%in% c(2050)) %>% 
  mutate(value = value) %>% 
  mutate(Protection= as.integer(gsub(" percent","",Protection)))->data_for_plot

low_avail_details <- read.csv("other_data/land_convertible.csv",stringsAsFactors = FALSE) %>% select(-Needed_unprotected_percent_convertible,-new_unmanaged) %>% 
          mutate(available=100-available)


needed <- read.csv("other_data/land_convertible.csv",stringsAsFactors = FALSE) %>% 
          select(-available,-Needed_unprotected_percent_convertible) %>% 
          distinct() %>% 
          mutate(new_unmanaged=100-new_unmanaged)

avail_managed <-  read.csv("other_data/available_managed.csv",stringsAsFactors = FALSE) %>% dplyr::select(-Needed_unprotected_percent_convertible,-needed_managed) %>% 
                  distinct() %>% 
                  mutate(new_managed= 100-new_managed) 


needed_managed <- read.csv("other_data/available_managed.csv",stringsAsFactors = FALSE) %>% 
                  dplyr::select(-Needed_unprotected_percent_convertible,-new_managed) %>% 
                  distinct() %>% 
                  mutate(needed_managed= 100-needed_managed)

data_for_plot %>% left_join(low_avail_details) %>% mutate(available= available) %>% 
  left_join(avail_managed, by = c("region")) %>% 
  left_join(needed, by = c("region","agg.land")) %>% 
  left_join(needed_managed, by =c("region")) %>% 
  mutate(new_unmanaged=if_else(is.na(new_unmanaged),needed_managed,new_unmanaged),
         available= if_else(is.na(available),new_managed,available))->data_for_plot


formatter1000 <- function(x){ 
    100-x 
}



intersection_points <- data_for_plot %>% 
                       group_by(region,agg.land) %>% 
                       mutate(diff = abs(available- Protection)) %>% 
                       filter(diff < 12) %>% 
                       mutate(value = mean(value),
                              Protection=available) %>% 
                       ungroup() %>% 
                       distinct()

intersection_points_needed <- data_for_plot %>% 
                       group_by(region,agg.land) %>% 
                       mutate(diff = abs(new_unmanaged- Protection)) %>% 
                       filter(diff < 12) %>% 
                       mutate(value = mean(value),
                              Protection=new_unmanaged) %>% 
                       ungroup() %>% 
                       distinct()

data_for_plot %>% filter(agg.land=="biomass")->biomass_data

g <- ggplot()+
   geom_point(data=intersection_points %>% na.omit() %>%  
                filter(region==region_select,!agg.land %in% c("rock and desert", "urban","desert")),
             aes(x=available,y=value,color=agg.land),size=4)+
  geom_point(data=intersection_points_needed %>% filter(region==region_select,!agg.land %in% c("rock and desert", "urban","desert")),aes(x=new_unmanaged,y=value,color=agg.land),show.legend = FALSE,shape=17,size=4) +
  geom_line(data=data_for_plot%>% 
               filter(region==region_select,
                      !agg.land %in% c("rock and desert", "urban","desert")),
            aes(x=Protection,y=value,color=agg.land,group=agg.land))+
  # geom_vline(data=data_for_plot %>% na.omit() %>% filter(region==region_select),aes(xintercept=available,color=agg.land), linetype = 3,size=2,show.legend = FALSE) +
  facet_wrap(~region,scales="free_y")+
  ylab("Marginal increase/decrease in Percent")+
  xlab("Availability")+
  ggtitle("Marginal increase/decrease in land allocation by land type in 2050 with increase in protection")+
  scale_color_lancet()+
  guides(color=guide_legend(title="Land type"))+
  scale_shape_manual(values=c(0,1,2))+scale_x_continuous(labels=formatter1000,breaks = seq(0,100,10),minor_breaks = seq(0,100,10))+
  labs(subtitle = "Dots are the starting percent of available land in 2015.Triangles are new percentage of available land after implementing 30 by 30 targets.")

g + scheme_basic+
  theme(axis.line = element_line(color='black'),
    plot.background = element_blank())

ggsave( paste0(output_path_images,"6.Change in land allocation in 2050 percent",project_name,toString(region_select),'.png'),width = 16, height = 14)

write.csv(data_for_plot, paste0(output_path_csv,"6. Marginal_plot_percent.csv"))


```

## Figure 6d: Marginal change in land allocation vs Marginal change in availability (Percent) all regions


```{r,fig.width=12, fig.height=8,echo=FALSE,message=FALSE, warning=FALSE}


g <- ggplot()+
   geom_point(data=intersection_points %>% na.omit() %>%  
                filter(!agg.land %in% c("rock and desert", "urban","desert")),
             aes(x=available,y=value,color=agg.land),size=2)+
  geom_point(data=intersection_points_needed %>% filter(!agg.land %in% c("rock and desert", "urban","desert")),aes(x=new_unmanaged,y=value,color=agg.land),show.legend = FALSE,shape=17,size=2) +
  geom_line(data=data_for_plot%>% 
               filter(!agg.land %in% c("rock and desert", "urban","desert")),
            aes(x=Protection,y=value,color=agg.land,group=agg.land))+
  # geom_vline(data=data_for_plot %>% na.omit() %>% filter(region==region_select),aes(xintercept=available,color=agg.land), linetype = 3,size=2,show.legend = FALSE) +
  facet_wrap(~region,scales="free_y")+
  ylab("Marginal increase/decrease in Percent")+
  xlab("Availability")+
  ggtitle("Marginal increase/decrease in land allocation by land type in 2050 with increase in protection")+
  scale_color_lancet()+
  guides(color=guide_legend(title="Land type"))+
  scale_shape_manual(values=c(0,1,2))+scale_x_continuous(labels=formatter1000,breaks = seq(0,100,10),minor_breaks = seq(0,100,10))+
  labs(subtitle = "Dots are the starting percent of available land in 2015.Triangles are new percentage of available land after implementing 30 by 30 targets.")

g + scheme_basic+
  theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    axis.text=element_text(size=10),
    strip.text.x = element_text(size = 8))

ggsave( paste0(output_path_images,"6.Change in land allocation in 2050 percent all regions",project_name,'.png'),width = 16, height = 14)


```



## Figure 7a: Irrigated bioenergy yields


```{r,fig.width=12, fig.height=8,echo=FALSE,message=FALSE, warning=FALSE}

shapefile <- read_sf("other_data/glu_boundaries_moirai_landcells_3p1_0p5arcmin.shp")

irrigated_bio_yields <- read.csv("other_data/L163.ag_irrBioYield_GJm2_R_GLU.csv",skip=4) %>% mutate(glu_id= as.numeric(gsub("GLU","",GLU))) %>% 
  group_by(glu_id) %>% 
  mutate(Yield_GJm2=mean(Yield_GJm2)) %>% 
  ungroup() %>% 
  dplyr::select(glu_id,Yield_GJm2) %>% 
  distinct()
shapefile %>% left_join(irrigated_bio_yields)->joined_file

g <- ggplot(data=joined_file)+
     geom_sf(aes(fill=Yield_GJm2))+
     scale_fill_viridis(option="magma")+
     ggtitle("Irrigated bioenergy yields by water basin in GJ/m2")

g

ggsave( paste0(output_path_images,"7.Irrigated bioenergy yields by water basin in GJ per m2",project_name,toString(region_select),'.png'),width = 16, height = 14)

```

## Figure 7b: Rainfed bioenergy yields


```{r,fig.width=12, fig.height=8,echo=FALSE,message=FALSE, warning=FALSE}

shapefile <- read_sf("other_data/glu_boundaries_moirai_landcells_3p1_0p5arcmin.shp")

rfd_bio_yields <- read.csv("other_data/L163.ag_rfdBioYield_GJm2_R_GLU.csv",skip=4) %>% mutate(glu_id= as.numeric(gsub("GLU","",GLU))) %>% 
  group_by(glu_id) %>% 
  mutate(Yield_GJm2=mean(Yield_GJm2)) %>% 
  ungroup() %>% 
  dplyr::select(glu_id,Yield_GJm2) %>% 
  distinct()
shapefile %>% left_join(rfd_bio_yields)->joined_file

g <- ggplot(data=joined_file)+
     geom_sf(aes(fill=Yield_GJm2))+
     scale_fill_viridis(option="magma")+
     ggtitle("Rainfed bioenergy yields by water basin in GJ/m2")

g

ggsave( paste0(output_path_images,"7b.Rainfed bioenergy yields by water basin in GJ per m2",project_name,toString(region_select),'.png'),width = 16, height = 14)

```




## THE END ##

